### 2015-10-05 pics/blue.tex
add all figures
add more pics

\addplot+[ycomb,
         mark=.,
         ultra thick,
         diplom2,
         forget plot
        ]
        table[
        x expr = \thisrowno{0},
        y expr = \thisrowno{1}
        ]
        {../data/blue_NeNe.dat};
        \addlegendimage{line legend, diplom2, very thick};
        \addlegendentry{blue};

%\addplot[
%         mark=none,
%         diplom2,
%         ultra thick,
%         %dotted
%         ]
%         table[
%         x expr=\thisrowno{0},
%         y expr=\thisrowno{1}
%         ]
%        {../data/xear_3_surf.dat_intadd.inp.sp};
%         \addlegendentry{1 Xe, 55 Ar};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\addplot+[ycomb,
         mark=.,
         ultra thick,
         blue,
         forget plot
        ]
        table[
        x expr = \thisrowno{0},
        y expr = \thisrowno{1}
        ]
        {../data/blue_NeNe.dat};
        \addlegendimage{line legend, blue, very thick};
        \addlegendentry{set 3 (blue)};

\draw[thick] (axis cs:1.45,0.003) arc [radius=0.80cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
     at (axis cs:1.1,0.0038) {};

\draw[thick] (axis cs:2.00,0.0078) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
     at (axis cs:2.0,0.0080) {};

\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]92:{\small across shells}}]
     at (axis cs:2.70,0.0010) {};

### 2015-10-05 pics/rot.tex
start full paper
add all figures
add more pics

\addplot+[ycomb,
         mark=.,
         ultra thick,
         diplom2,
         forget plot
        ]
        table[
        x expr = \thisrowno{0},
        y expr = \thisrowno{1}
        ]
        {../data/blue_NeNe.dat};
        \addlegendimage{line legend, diplom2, very thick};
        \addlegendentry{blue};

%\addplot[
%         mark=none,
%         diplom2,
%         ultra thick,
%         %dotted
%         ]
%         table[
%         x expr=\thisrowno{0},
%         y expr=\thisrowno{1}
%         ]
%        {../data/xear_3_surf.dat_intadd.inp.sp};
%         \addlegendentry{1 Xe, 55 Ar};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\addplot+[ycomb,
         mark=.,
         ultra thick,
         red,
         forget plot
        ]
        table[
        x expr = \thisrowno{0},
        y expr = \thisrowno{1}
        ]
        {../data/red_NeNe.dat};
        \addlegendimage{line legend, red, very thick};
        \addlegendentry{set 5 (red)};

\draw[thick] (axis cs:1.40,0.007) arc [radius=0.77cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
     at (axis cs:1.0,0.0080) {};

\draw[thick] (axis cs:1.90,0.0120) arc [radius=0.55cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
     at (axis cs:1.9,0.0125) {};

\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]92:{\small across shells}}]
     at (axis cs:2.70,0.0010) {};
